Considering scale in multilayer animal social networks

### 2020-06-11 paper/manuscript.Rmd
adjust input DT
adjust fig paths

library(data.table)
DT <- readRDS('../data/derived-data/1-sub-seasons-fogo-caribou.Rds')
```

@@

```{r spacetime, fig.cap='(ref:spacetime)'}
knitr::include_graphics('../graphics/figure1.png')
```

@@

```{r socres, fig.cap='(ref:socres)'}
knitr::include_graphics('../graphics/figure-spatialthreshold.png')
```

@@

```{r lcres, fig.cap='(ref:lcres)'}
knitr::include_graphics('../graphics/figure-lcres.png')
```

@@

```{r nobs, fig.cap='(ref:nobs)'}
knitr::include_graphics('../graphics/figure-nobs.png')
```

@@

```{r winlen, fig.cap='(ref:winlen)'}
knitr::include_graphics('../graphics/figure-winlength.png')
```

```{r winpos, fig.cap='(ref:winpos)'}
knitr::include_graphics('../graphics/figure-winpos.png')
```

>>>>

library(data.table)
DT <- readRDS('../data/derived-data/01-sub-fogo-caribou.Rds')
```

@@

```{r spacetime, fig.cap='(ref:spacetime)'}
knitr::include_graphics('../graphics/figure-1.png')
```

@@

```{r lcres, fig.cap='(ref:lcres)'}
knitr::include_graphics('../graphics/figure-3.png')
```

@@

<!-- TODO: fix to temp -->
```{r winlen, fig.cap='(ref:winlen)'}
knitr::include_graphics('../graphics/figure-4.png')
```

@@

```{r socres, fig.cap='(ref:socres)'}
knitr::include_graphics('../graphics/figure-5.png')
```

@@

```{r nobs, fig.cap='(ref:nobs)'}
knitr::include_graphics('../graphics/figure-6.png')
```
